\myshort{} to Enable Systematic Evaluation of Testing Techniques

### 2025-04-24 paper/main.tex
Updated venv to conda

\begin{table}
  \centering
  \small
  \caption{\label{table:bug-characterization}Characterization of
    bugs from \tname.}
  \vspace{-1ex}
  %%   \Fix{Is this up to date? I have seen
  %% lots of activity recently but these numbers remain the
  %% same - Fixed (Abid)}\Fix{Can we add info about whether Python and/or C code causes
  %%     the bug? - Abid: we report how many c,python and cuda native files are buggy in total but not per bug, so currently no}\Fix{Can we add info on whether it is GPU related
  %%     (i.e., only manifests in GPUs)? - Abid: venv-docker is the same
  %%     as cpu-gpu}}
  \begin{tabular}{l|rrr}
  \toprule & \multirow{2}{*}{\#} & \multicolumn{1}{r}{build} &
  \multicolumn{1}{r}{enviroment} \\ & & release-nightly & venv-docker
  \\ \cmidrule(lr){2-4} \jax{} & 46 & 45-1 & 45-1 \\ \torch{} & 37 &
  18-19 & 21-16 \\ \tf{} & 29 & 27-2 & 29-0 \\ \midrule
  \multicolumn{1}{c|}{$\Sigma$} & \numbugs{} & 90-22& 95-17
  \\ \bottomrule
  \end{tabular}
  \vspace{-2ex}  
\end{table}

@@

\tname\ contains \numbugs{} instances of reproducible bugs
representing three popular DL libraries, namely, \jax, \tf, and
\torch. Table~\ref{table:bug-characterization} shows the list of bug
instances for each supported library. Column ``\#'' shows the number
of bug instances, column ``build'' shows the breakdown of instances
for each kind of build (release or nightly), and column
``environment'' shows the breakdown of instances for each kind of
environment to reproduce the bug (venv or docker). Co-incidentally,
all bugs that require a GPU are reproduced using docker
containers, i.e. the column venv-docker matches what would have been
observed with a column CPU-GPU, to indicate if the bug can be
reproduced with a CPU or if it requires a
GPU. Table~\ref{table:bug-stats} shows the breakdown error types for
the bugs in our dataset. The row ``Incorrect Output'' is listed first
as it requires a distinct kind of oracle comparing consistency of the
outputs of test runs on a CPU and on GPU. In total, we have
\numbugtypes\ different types of bug manifestations across the three
libraries.

>>>>

\begin{table}
  \centering
  \small
  \caption{\label{table:bug-characterization}Characterization of
    bugs from \tname.}
  \vspace{-1ex}
  %%   \Fix{Is this up to date? I have seen
  %% lots of activity recently but these numbers remain the
  %% same - Fixed (Abid)}\Fix{Can we add info about whether Python and/or C code causes
  %%     the bug? - Abid: we report how many c,python and cuda native files are buggy in total but not per bug, so currently no}\Fix{Can we add info on whether it is GPU related
  %%     (i.e., only manifests in GPUs)? - Abid: venv-docker is the same
  %%     as cpu-gpu}}
  \begin{tabular}{l|rrr}
  \toprule & \multirow{2}{*}{\#} & \multicolumn{1}{r}{build} &
  \multicolumn{1}{r}{enviroment} \\ & & release-nightly & conda-docker
  \\ \cmidrule(lr){2-4} \jax{} & 46 & 45-1 & 45-1 \\ \torch{} & 37 &
  18-19 & 21-16 \\ \tf{} & 29 & 27-2 & 29-0 \\ \midrule
  \multicolumn{1}{c|}{$\Sigma$} & \numbugs{} & 90-22& 95-17
  \\ \bottomrule
  \end{tabular}
  \vspace{-2ex}  
\end{table}

@@

\tname\ contains \numbugs{} instances of reproducible bugs
representing three popular DL libraries, namely, \jax, \tf, and
\torch. Table~\ref{table:bug-characterization} shows the list of bug
instances for each supported library. Column ``\#'' shows the number
of bug instances, column ``build'' shows the breakdown of instances
for each kind of build (release or nightly), and column
``environment'' shows the breakdown of instances for each kind of
environment to reproduce the bug (conda enviroment or docker). Co-incidentally,
all bugs that require a GPU are reproduced using docker
containers, i.e. the column conda-docker matches what would have been
observed with a column CPU-GPU, to indicate if the bug can be
reproduced with a CPU or if it requires a
GPU. Table~\ref{table:bug-stats} shows the breakdown error types for
the bugs in our dataset. The row ``Incorrect Output'' is listed first
as it requires a distinct kind of oracle comparing consistency of the
outputs of test runs on a CPU and on GPU. In total, we have
\numbugtypes\ different types of bug manifestations across the three
libraries.
